Tables

### 2018-05-17 code/figures.rmd
Formatting tables and figures + new draft with method

Should I first run MA and then transform effect sizes? ->Not sure how how to treat the raw mean differences, since I only get the MA-estimate estimate and the SE.  More straightforward to convert to common metric first. **Kolden + Ihle give formulas.**

@@

#For mean differrence + SD
transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #taken from Kolden from Esther
  d <- (m1 - m2) / sdpooled
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes
  r <- d / sqrt(d^2 + corr)
  data.frame(r = r, n = n1 + n2)
}

#For Risk difference/OR
transform_RD <- function(ai, bi, ci, di){
  ai <- ifelse(ai == 0, 0.5, ai)  #If value is equal to zero add one half so as to not divide by zero
  bi <- ifelse(bi == 0, 0.5, bi)  #This affects 1 study for Allowed vs. forbidden
  ci <- ifelse(ci == 0, 0.5, ci)  #And several studies for Low vs. high category scales
  di <- ifelse(di == 0, 0.5, di)
  logOR <- log((ai*di) / (bi*ci))
  d = logOR * sqrt(3)/pi
  n1 = ai + bi
  n2 = ci + di
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes
  r <- d / sqrt(d^2 + corr)
  data.frame(r = r, n = ai + bi + ci +di)
}

@@

```{r MA_df}
summarizer <- function(x){
  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, test = "knha", data = x) #takes raw correlation as input
  data.frame(z = fit$b[[1]], I2 = fit$I2, H2 = fit$H2, H2alt = fit$QE / fit$k) #estimate out
}
#Alternative version of calculating I2 does not make conceptual sense because gives negative values. Alternative method for calculating H2 provides information also on excessive homogeneity (i.e, less variability than expected by chance) for those interested. (that is, does not have a lower limit of 1)

@@

ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  ggtitle("I2 increases with effect size in pre-registered multi-lab studies") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.1, y = 75, label = "b = 69.40, R2 = 0.61", size = 3.5)

@@

ggplot(res2, aes(x = z, y = H2alt)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  ggtitle("H2 increases with effect size in pre-registered multi-lab studies") +
  xlab("Fisher's z") +
  geom_text(x = 0.1, y = 6, label = "b = 3.81, R2 = 0.53", size = 3.5)

>>>>

Should I first run MA and then transform effect sizes? ->Not sure how how to treat the raw mean differences, since I only get the MA-estimate estimate and the SE.  More straightforward to convert to common metric first. **Kolden + Ihle give formulas.** From book Cooper & Hedges, 1994.

@@

#For mean differrence + SD
transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #page 226. 
  d <- (m1 - m2) / sdpooled
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes, p.234
  r <- d / sqrt(d^2 + corr) #p. 234
  data.frame(r = r, n = n1 + n2)
}

#For Risk difference/OR
transform_RD <- function(ai, bi, ci, di){
  ai <- ifelse(ai == 0, 0.5, ai)  #If value is equal to zero add one half so as to not divide by zero
  bi <- ifelse(bi == 0, 0.5, bi)  #This affects 1 study for Allowed vs. forbidden
  ci <- ifelse(ci == 0, 0.5, ci)  #And several studies for Low vs. high category scales
  di <- ifelse(di == 0, 0.5, di)
  logOR <- log((ai*di) / (bi*ci)) #p. 266
  d = logOR * sqrt(3)/pi #p. 232
  n1 = ai + bi
  n2 = ci + di
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes, p. 234
  r <- d / sqrt(d^2 + corr) #p. 234
  data.frame(r = r, n = ai + bi + ci +di)
}

@@

```{r MA_df}
summarizer <- function(x){
  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, test = "knha", data = x) #takes raw correlation as input
  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / fit$k) #estimate out
}
#Alternative version of calculating I2 does not make conceptual sense because gives negative values. Alternative method for calculating H2 provides information also on excessive homogeneity (i.e, less variability than expected by chance) for those interested. (that is, does not have a lower limit of 1)

@@

I2 <- ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.15, y = 80, label = "b = 69.40, R2 = 0.61", size = 3.5) +
  theme_classic()

@@

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  geom_text(x = 0.14, y = 6, label = "b = 3.81, R2 = 0.53", size = 3.5) +
  theme_classic()

# ggsave("H2_effect_size.png")
library(cowplot)

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v")
# save_plot("effect_het.png", effect_het,
          # nrow = 2, base_aspect_ratio = 1.3)

### 2018-05-17 code/tables.rmd
Formatting tables and figures + new draft with method

@@

summary.table <- dat %>% 
  group_by(rs) %>% 
  summarize(Labs = n_distinct(Site),
            Countries = n_distinct(country), 
            Effects = n_distinct(effect),
            Participants = if(Effects == 1){sum(Ntotal)}
                           else{sum(Ntotal) / Effects}) %>% #average across effects
  rename(Study = rs)

summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE,
           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).")
```

@@

  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
             p = fit$pval,
             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
}

@@

#Add rs to the data-frame
het <- dat %>% 
  select(rs, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Std. mean diff.",
                              r = "Correlation",
                              'Raw mean difference' = "Raw mean diff.")) %>% 
  arrange(desc(s_I2)) #sort by I2 for standardized effect
```

##Heterogeneity in preregistered multi-lab psychology studies
```{r heterogeneity-table}
library(kableExtra)
het %>% knitr::kable("latex", booktabs = T, digits = 2, col.names = c("RS", "Effect", "Effect type", "Estimate", "p-value", "I2(%)", "ci.lb", "ci.ub")) %>% 
  kable_styling() %>%
  footnote(threeparttable = TRUE,
           general = "We meta-analyzed effects using the same outcome measures that were used by the original authors. Standardized mean difference is Hedge's g. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. Effects were estimated in metafor using REML with the 'knha' correction. Estimate column are point estimates of effect sizes. Final columns are the upper and lower boundaries of the 90% confidence interval for I2.")

>>>>

##Heterogeneity increases with effect size
```{r effect-size-heterogeneity-table}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.8, .7,.6), 3), ncol = 3)
rho <- c(0, .5, .8)
rel <- c("R = .8", "R = .7", "R = .6")

rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
diff_row <- data.frame(rel = "Diff.", X1 = 0, X2 = 0.05, X3 = 0.08)

het_demo <- data.frame(rel, rooted_relabilities)
het_demo <- rbind(het_demo, diff_row)

het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "Rho = 0", "Rho = .5", "Rho = .8")) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE) %>% 
  row_spec(3, hline_after = T)

@@

#Shortened version of APA reference
papers <- c('Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Jr., Bahník, S., Bernstein, M. J., . . . Nosek, B. A. (2014). Investigating variation in replicability: A "many labs" replication project.', 
'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011).',
'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect.',
'Cheung, I., Campbell, L., LeBel, E. P., Ackerman, R. A., Aykutoglu, B., Bahník, S., ... & Carcedo, R. J. (2016). Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).',
'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988).',
'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
"O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998)")

##Full APA reference below
# c('Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Jr., Bahník, S., Bernstein, M. J., . . . Nosek, B. A. (2014). Investigating variation in replicability: A "many labs" replication project. Social Psychology, 45(3), 142-152.', 
# 'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication. Journal of Experimental Social Psychology, 67, 68-82.',
# 'Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., ... & Brown, E. R. (2016). Many Labs 3: Evaluating participant pool quality across the academic semester via replication. Journal of Experimental Social Psychology, 67, 68-82.',
# 'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990). Perspectives on Psychological Science, 9(5), 556-578.',
# 'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011). Perspectives on Psychological Science, 11(1), 158-171.',
# 'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect. Perspectives on Psychological Science, 11(4), 546-573.',
# 'Cheung, I., Campbell, L., LeBel, E. P., Ackerman, R. A., Aykutoglu, B., Bahník, S., ... & Carcedo, R. J. (2016). Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002). Perspectives on Psychological Science, 11(5), 750-764.',
# 'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988). Perspectives on Psychological Science, 11(6), 917-928.',
# 'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012). Perspectives on Psychological Science, 12(3), 527-542.',
# "O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998): Multilab direct replication of: A variant of study 4 from Dijksterhuis, A., & van Knippenberg, A.(1998). The relation between perception and behavior, or how to win a game of trivial pursuit. Journal of personality and social psychology. Perspectives on Psychological Science."

summary.table <- dat %>% 
  group_by(rs) %>% 
  summarize(k = n_distinct(Site),
            Countries = n_distinct(country), 
            Effects = n_distinct(effect),
            Participants = if(Effects == 1){sum(Ntotal)}
                           else{sum(Ntotal) / Effects}) %>% #average across effects
  mutate(Paper = papers) %>% 
  select(RS = rs, Paper, everything()) #change order of columns

summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
  kable_styling() %>% 
  column_spec(2, width = "25em") %>% #specify width of paper column
  footnote(threeparttable = TRUE,
           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. Participant numbers are those used for primary analyses by original authors (i.e., after exclusions). RS = Replication Study, k = no. primary studies, ML = Many Labs, RRR = Registered Replication Report.")
```

@@

  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
}

@@

#Add rs to the data-frame
het <- dat %>% 
  select(rs, Site, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>% 
  select(rs, effect,k , everything()) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
```

##Heterogeneity in preregistered multi-lab psychology studies
```{r heterogeneity-table}
library(kableExtra)

het %>% knitr::kable("latex", align = "c", booktabs = TRUE,digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Size", "I2(%)", "ci.lb", "ci.ub")) %>% 
  kable_styling("scale_down") %>%
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "We meta-analyzed effects using the same outcome measures that were used by the original authors. Standardized mean difference is Hedge's g. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. Effects were estimated in metafor using REML with the 'knha' correction. RS = Replication Study, k = no. primary studies, Size = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.")
